Prospects of detecting gamma-ray emission from galaxy clusters: cosmic rays and dark matter annihilations

### 2011-04-22 paper.tex
update

\begin{figure}%[t]
 \includegraphics[width=0.99\columnwidth]{figures/fit.porter.v2.eps}
\caption{\it Spectral dependence of radiation fields in a cluster of
  galaxies. The black dotted line in the left peak show the spectrum
  of CMB photons using a black body with a temperature of
  $2.73$~K. The crosses in the middle and right peaks represent the
  measured spectra from stars and dust (SD), respectively, and are
  derived in \cite{2006ApJ...648L..29P} for a galaxy. We normalize the
  individual SD spectrum separately using the observed luminosity from
  SD in clusters. The SD luminosity is related to the cluster mass
  through Eqns.~(\ref{eq:N_stars}-\ref{eq:u_SD}), where we use have
  used the mass $\mvir=10^{15}\msun$ in this figure. Finally we
  renormalize the SD spectra to the radius $r=0.03\rvir$, where the
  smooth energy density of the SD light (see Fig.~\ref{fig:SD_Edens})
  equals the energy density of the CMB. The red dashed lines show the
  fitted SD spectral model.}
 \label{fig:SD_spectra}
\end{figure}
\begin{figure}%[t]
 \includegraphics[width=0.99\columnwidth]{figures/ucool.eps}
 \caption{\it Spatial dependence of the energy density of radiation
   fields in a cluster of galaxies. The energy density of the CMB,
   shown by the blue dotted line, is isotropic throughout the cluster,
   hence represented by a flat profile with
   $u_\rmn{cmb}=0.26\,\rmn{eV}\,\rmn{cm}^{-3}$. The energy density of
   the light from stars and dust (SD) is denoted by the red dashed
   line and the solid purple line for the total SD light and the
   smooth SD light, respectively. For comparison we show the energy
   density of the stars and a low dust model (SLD) with the light blue
   line. The SD light has been renormalized to a cluster with the mass
   $\mvir=10^{15}\msun$. Finally we show the energy density two
   magnetic field models with a central magnetic field of 3~$\mu
   G$. The magnetic field scales with the gas density to the power
   $\alpha_\rmn{B}$; green dash-dotted line ($\alpha_\rmn{B}=0.5$) and
   orange dash-dotted line ($\alpha_\rmn{B}=0.7$). Note that the SD
   radiation is dominating the energy density inside
   $\sim0.1\,\rvir$.}
 \label{fig:SD_Edens}
\end{figure}

@@

\begin{figure*}
\begin{minipage}{2.0\columnwidth}
 \includegraphics[width=0.49\columnwidth]{figures/flux.BMcompI.v11.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompJ.v11.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompK.v11.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompJs.v11.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
\caption{\it Comparing the differential flux from different models: we
  show the continuum emission from DM benchmark (BM) models (blue
  dashed), electrons and positrons from DM BM models that inverse
  Compton upscattered both CMB photons (orange dash-dotted) as well as
  dust and star photons (green dotted), and CRp induced gamma-ray
  emission (red solid). Each panel is associated with an individual DM
  BM model; upper left $\Ip$, lower left $\Kp$, upper right $\Jp$, and
  lower right $\Js$. The emission is calculated for the Fornax cluster
  using a point spread function of $0.1\deg$ and a boost from
  substructures of 570. We find bright prospects for detecting the
  continuum emission that is dominating the total emission in the GeV
  energy range. Also note that, above 100~MeV the total inverse
  Compton emission is at least a factor 10 smaller than the emission
  expected from both the continuum emission and the emission coming
  from CRps.}
 \label{fig:diff_BM}
\end{minipage}
\end{figure*}

>>>>

\begin{figure}%[t]
 \includegraphics[width=0.99\columnwidth]{figures/fit.porter.v2.eps}
\caption{\it Spectral dependence of radiation fields in a cluster of
  galaxies. The black dotted line in the left peak show the spectrum
  of CMB photons using a black body with a temperature of
  $2.73$~K. The crosses in the middle and right peaks represent the
  measured spectra from stars and dust (SD), respectively, and are
  derived in \cite{2006ApJ...648L..29P} for a galaxy. We normalize the
  individual SD spectrum separately using the observed luminosity from
  SD in clusters. The SD luminosity is related to the cluster mass
  through Eqns.~(\ref{eq:u_SD}-\ref{eq:N_stars}), where we use have
  used the mass $\mvir=10^{15}\msun$ in this figure. Finally we
  renormalize the SD spectra to the radius $r=0.03\rvir$, where the
  smooth energy density of the SD light (see Fig.~\ref{fig:SD_Edens})
  equals the energy density of the CMB. The red dashed lines show the
  fitted SD spectral model.}
 \label{fig:SD_spectra}
\end{figure}
\begin{figure}%[t]
 \includegraphics[width=0.99\columnwidth]{figures/ucool.eps}
 \caption{\it Spatial dependence of the energy density of radiation
   fields in a cluster of galaxies. The energy density of the CMB,
   shown by the blue dotted line, is isotropic throughout the cluster,
   hence represented by a flat profile with
   $u_\rmn{cmb}=0.26\,\rmn{eV}\,\rmn{cm}^{-3}$. The energy density of
   the light from stars and dust (SD) is denoted by the red dashed
   line and the solid purple line for the total SD light and the
   smooth SD light, respectively. For comparison we show the energy
   density of the stars and a low dust model (SLD) with the light blue
   line. The SD light has been renormalized to a cluster with the mass
   $\mvir=10^{15}\msun$. Finally we show the energy density two
   magnetic field models with a central magnetic field of 3~$\mu
   G$. The magnetic field scales with the gas density to the power
   $\alpha_\rmn{B}$; green dash-dotted line ($\alpha_\rmn{B}=0.5$) and
   orange dash-dotted line ($\alpha_\rmn{B}=0.7$). Note that the SD
   radiation is dominating the energy density inside
   $\sim0.1\,\rvir$.}
 \label{fig:SD_Edens}
\end{figure}

@@

\begin{figure*}
\begin{minipage}{2.0\columnwidth}
 \includegraphics[width=0.49\columnwidth]{figures/flux.BMcompI.v11.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompJ.v11.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompK.v11.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompJs.v11.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
\caption{\it Comparing the differential flux from different models: we
  show the continuum emission from DM benchmark (BM) models (blue
  dashed), electrons and positrons from DM BM models that inverse
  Compton upscattered both CMB photons (orange dash-dotted) as well as
  dust and star photons (green dotted), and CRp induced gamma-ray
  emission (red solid). Each panel is associated with an individual DM
  BM model; upper left $\Ip$, lower left $\Kp$, upper right $\Jp$, and
  lower right $\Js$. The emission is calculated for the Fornax cluster
  using a point spread function of $0.1\deg$ and a boost from
  substructures of 570 (ADD SUBBOOST ON SD MODEL, SHOULD BE ONLY FACTOR
  FEW). We find bright prospects for detecting the continuum emission
  that is dominating the total emission in the GeV energy range. Also
  note that, above 100~MeV the total inverse Compton emission is at
  least a factor 10 smaller than the emission expected from both the
  continuum emission and the emission coming from CRps.}
 \label{fig:diff_BM}
\end{minipage}
\end{figure*}
